---
title: "Challenge 4"
title-block-banner: slateblue
author: "Anagha Sikha"
format: 
  html:
    code-fold: true
    theme: minty
    self-contained: true
editor: visual
execute: 
  echo: true
  error: true
---

# Challenge

### Load-In

```{r setup}
#| message: false
library(tidyverse)
library(here)
library(moderndive)
library(forcats)
```

### Reading the Data into R

```{r reading data}
#| message: false
# Code for question 1! 
avocado <- read_csv(here::here("supporting_artifacts", 
                               "extended_learning", 
                               "Challenge 4",
                               "avocado.csv"))
```

### Avocado Dataset

```{r}
avocado |>
    distinct(region, keep_all = TRUE)
avocado_clean <- avocado|>
  rename(total_volume = `Total Volume`,
         total_bags = `Total Bags`,
         large_HASS = '4225',
         small_HASS = '4046',
         xl_HASS = '4770')
```

### Avocado California Dataset

```{r}
CA_cities <- data.frame(region = c('LosAngeles', 'SanDiego', 'Sacramento', 'SanFrancisco'))
avocado_CA <- avocado_clean |>
  semi_join(CA_cities, by = "region") 
```

### CA Housing Prices Dataset

```{r housing_dataset}
CA_housing_prices <- 
  data.frame(region = c("LosAngeles","LosAngeles", "LosAngeles", "LosAngeles",
                        "Sacramento","Sacramento","Sacramento","Sacramento",
                        "SanDiego", "SanDiego", "SanDiego","SanDiego",
                        "SanFrancisco","SanFrancisco","SanFrancisco","SanFrancisco"),
             average_annual_price = c(562072.833, 605461.75, 647423.916, 700454.67, #LA
                                245447.83, 272402.25, 300190.67,325170.67, #SAC
                                497316.166, 529688.25,567404.75,611114.33, #SD
                                1109257.17, 1190377.17, 1227453.08, 1358550.58), #SF
              year = c("2015","2016","2017","2018",
                        "2015", "2016", "2017","2018",
                        "2015", "2016", "2017","2018",
                        "2015", "2016", "2017","2018")
              ) |>
  mutate(year = as.numeric(year))

# median house price LA: https://www.zillow.com/home-values/12447/los-angeles-ca/
# median house price SD: https://www.zillow.com/home-values/54296/san-diego-ca/
# median house price Sac: https://www.zillow.com/home-values/20288/sacramento-ca/
# median house price SF: https://www.zillow.com/home-values/20330/san-francisco-ca/
```

## Joining Datasets

```{r joined_dataset}
#| message: false
joined_dataset <- avocado_CA |>
  left_join(CA_housing_prices, by = c("region" = "region", "year" = "year")) |>
  select(region, year, average_annual_price, AveragePrice, total_volume) |>
  group_by(region, year) |>
  summarize(average_avocado_prices = round(mean(AveragePrice), 2),
             average_avocado_volume = mean(total_volume),
             average_house_prices = mean(average_annual_price))
```

## Plots

```{r avocado_housing_plot}
#| message: False
joined_dataset |>
  #by house and avocado prices 
  mutate(year = as.factor(year)) |>
  ggplot(mapping = aes(average_avocado_prices, 
                       average_house_prices)) + 
  geom_point(aes(color = region,
                 shape = year)) + 
  labs(x = "Average Avocado Price ($)",
       y = "Average Housing Prices ($)") +
  geom_smooth(method = 'lm', se = FALSE, color = 'darkgray')

#by volume and house prices
joined_dataset |>
  mutate(year = as.factor(year)) |>
  ggplot(mapping = aes(average_avocado_volume, 
                       average_house_prices)) + 
  geom_point(aes(color = region,
                 shape = year)) + 
  labs(x = "Average Avocado Volume",
       y = "Average Housing Prices ($)") +
  geom_smooth(method = 'lm', se = FALSE, color = 'darkgray')

price_housing_cor <- ungroup(joined_dataset)|>
  get_correlation(formula = average_house_prices ~ average_avocado_prices)

volume_housing_cor <- ungroup(joined_dataset)|>
  get_correlation(formula = average_house_prices ~ average_avocado_volume)

# Resource: http://www.sthda.com/english/wiki/ggplot2-scatter-plots-quick-start-guide-r-software-and-data-visualization
# https://rdrr.io/cran/moderndive/man/get_correlation.html
```

Based on my two plots, I believe that there is not a relationship between house prices and avocado prices/sales.

From the first plot, which is a scatterplot measuring the average avocado prices and average house prices in the 4 regions of California (Los Angeles, Sacramento, San Diego, San Francisco) over the years of 2015 to 2018, we can see that there is distance from the points and the line of best fit. After calculating the correlation which is 0.401, we see that there is not a strong relationship between average avocado prices and average house prices.

From the second plot, which is a scatterplot measuring the average avocado sales and average house prices in the 4 regions of California (Los Angeles, Sacramento, San Diego, San Francisco) over the years of 2015 to 2018, we can see that there is a larger distance from the points and the line of best fit. After calculating the correlation which is 0.0761 we see that there is a very weak relationship between average avocado prices and average house prices.

From these two plots we see that spending money on avocados does not relate to millennials not being able afford houses.
