---
title: "Challenge 9"
title-block-banner: "#9370DB"
author: "Anagha Sikha"
format: 
  html:
    code-fold: true
    theme: minty
    self-contained: true
editor: visual
execute: 
  echo: true
  error: false
---

### Set Up {style="color: #b19cd9;"}

```{r setup}
#| message: false
library(tidyverse)
library(here)
library(DT)
library(kableExtra)
library(ggtext)

state_names_A <- read_csv(here::here("supporting_artifacts", 
                                     "extended_learning", 
                                     "Challenge 9", 
                                     "StateNames_A.csv"))
```

## Dataset Interactive Preview {style="color: #4B0082"}

```{r dataset-interactive}
#| message: false
head(state_names_A, 100) |>
  datatable(options = list(),
            class = "cell-border stripe",
            colnames = c('Number of Babies' = 'Count'),
            caption =  "TABLE 1: Number of U.S. Babies With Names Starting With A"
            )
```

## Summarizing & Visualizing Number of Allisons {style="color: #4B0082"}

### Question 1 {style="color: #b19cd9;"}

```{r allisons-Q1}
#| message: false
all_allisons <- state_names_A |> 
  rename(Sex = 'Gender')|>
  filter(Name == 'Allison') |>
  group_by(State, Sex) |> 
  summarize(total_num = sum(Count)) |> 
  pivot_wider(names_from = Sex,
              values_from = total_num) |> 
  rename(Total_Num_Female = 'F',
         Total_Num_Male = 'M') |> 
  mutate(across(.cols = Total_Num_Female:Total_Num_Male,
                .fns = ~replace_na(.,0))
         ) |> 
  kable(table.attr = "class=\"striped\"",
        format = "html",
        col.names = c('State', 
                      'Number of Female Babies',
                      'Number of Male Babies'),
        caption = "TABLE 2: Number of U.S. Babies with the Name 'Allison'"
        ) |> 
  kable_styling(bootstrap_options = "striped")
all_allisons
```

### Question 2 {style="color: #b19cd9;"}

```{r allsion-Q2}
#| message: false
female_allisons <- state_names_A |> 
  rename(Sex = 'Gender')|>
  filter(Name == 'Allison',
         Sex == 'F') |> 
  group_by(Year) |>
  summarize(Total_Num = sum(Count))
```

### Question 3 {style="color: #b19cd9;"}

```{r allison-Q3}
#| message: false
female_allisons |>
  ggplot(mapping = aes(x = Year,
                       y = Total_Num)
         ) +
  labs(x = "Year",
       title = 'Number of Female U.S. Babies Named "Allison" Over Time',
       subtitle = "From 1997 to 2014"
       ) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 7)) +
  scale_x_continuous(breaks = seq(from = 1997, to = 2014, by = 1)) +
  geom_line(color = '#9370DB')
```

## Modeling the Number of Allisons {style="color: #4B0082"}

### Question 4 {style="color: #b19cd9;"}

```{r allison-Q4}
num_allisons_lm <- female_allisons |> 
  #all the allisons per year
  lm(Total_Num ~ Year, data = _)
num_allisons_lm
```

### Question 5 {style="color: #b19cd9;"}

```{r allison-Q5}
#| message: false
female_allisons |> 
  ggplot(aes(x = Year, y = Total_Num)) +
  geom_point(color = '#4B0082') +
  stat_smooth(method = "lm") + 
  labs(title = 'Number of Babies Named "Allison" vs Time (Year)',
       subtitle = "From 1997 to 2014") +
  theme(axis.title.y = element_blank(),
       axis.title.x = element_blank(),
       axis.text.x = element_text(size = 7)) +
  scale_x_continuous(breaks = seq(from = 1997, to = 2014, by = 1))
```

### Question 6 {style="color: #b19cd9;"}

##### **Predicted Number of Allison's = 209689.8 - 101.5 (Year)**

### Question 7 {style="color: #b19cd9;"}

```{r allison-Q7}
#| message: false
num_allisons_lm |> 
  broom::augment() |> 
  ggplot(mapping = aes(y = .resid,
                       x = .fitted)) +
  geom_point(color = '#4B0082') + 
  labs(title = "Predicted Number vs Residual Number of Allison's Over Time",
       subtitle = "From 1997 to 2014") +
  theme(axis.title.y = element_blank(),
       axis.title.x = element_blank(),
       axis.text.x = element_text(size = 7))
```

##### Patterns: From the residual plot, we see that the points are randomly scattered around the residual line (y = 0). There are no significant patterns.

### Question 8 {style="color: #b19cd9;"}

##### From this regression model, we see that there is a negative slope. We see that for every one year increase, there are around 101.5 less babies named Allison.

## Spelling By State {style="color: #4B0082"}

### Question 1 {style="color: #b19cd9;"}

```{r allan-Q1}
#| message: false
purple <- c("#CCCCFF", "#7B68EE", "#4B0082")

#filtered Dataset
male_allan <- state_names_A |> 
  rename(Sex = 'Gender')|>
  filter(Name == 'Allan' | Name == 'Alan' | Name == 'Allen',
         Sex == 'M')

#graph
male_allan |>
  group_by(Year, Name) |> 
  summarize(Total_Num = sum(Count)) |> 
  ggplot(mapping = aes(x = Year,
                       y = Total_Num,
                       color = Name)
         ) +
  labs(x = "Year",
       title = str_c("Number of Male U.S. Babies Named ",
                     "<span style = 'color:#CCCCFF'>**Alan**</span>",
                     ", <span style = 'color:#7B68EE'>**Allan**</span>",
                     ", and <span style = 'color:#4B0082'>**Allen**</span>"),
       subtitle = "From 1997 to 2014"
       ) +
  theme(plot.title = element_markdown(),
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 7),
        legend.position = "none") +
  scale_x_continuous(breaks = seq(from = 1997, to = 2014, by = 1)) +
  geom_line() +
  scale_color_manual(values = purple)
```

### Question 2 {style="color: #b19cd9;"}

```{r allan-Q2}
#| message: false
states_male_allan <- male_allan |>
  filter(State == 'CA' | State == 'PA',
         Year == 2000) |> 
  mutate(Count = replace_na(Count, 0)) |> 
  group_by(State, Name) |> 
  summarize(Total_Num = sum(Count)) |> 
  pivot_wider(names_from = Name,
              values_from = Total_Num
              )
# cannot pipeline because next question uses this dataset
kable(states_male_allan,
      format = "html",
        col.names = c('State', 
                      'Number of Alan',
                      'Number of Allan',
                      'Number of Allen'),
        align = 'r',
        caption = "TABLE 3: Number of Male Babies Named Alan, Allan, or Allen in California and Pennsylvania"
        )  |> 
  kable_styling(bootstrap_options = "striped")
```

### Question 3 {style="color: #b19cd9;"}

```{r allan-Q3}
#| message: false
ca_pa_male_allan <- states_male_allan |>
  rename(Allan_Count = 'Allan',
         Allen_Count = 'Allen',
         Alan_Count = 'Alan') |> 
  mutate(
    Total_Count = Alan_Count + Allan_Count + Allen_Count,
    Alan_Count = round((Alan_Count/Total_Count) * 100, 2),
    Allan_Count = round((Allan_Count/Total_Count) * 100, 2),
    Allen_Count = round((Allen_Count/Total_Count) * 100, 2)
    ) |> 
  select(-Total_Count) |> 
  kable(format = "html",
        col.names = c('State', 
                      'Percentage of Alan',
                      'Percentage of Allan',
                      'Percentage of Allen'),
        caption = "TABLE 4: Percentage of Male Babies Named Alan, Allan, or Allen in California and Pennsylvania"
        ) |> 
  kable_styling(bootstrap_options = "striped")
ca_pa_male_allan 
```

# Part 2

```{r}
#| message: false
# Spicing up Spelling By State Question 2
states_male_allan <- male_allan |>
  filter(State == 'CA' | State == 'PA',
         Year == 2000) |> 
  mutate(Count = replace_na(Count, 0)) |> 
  group_by(State, Name) |> 
  summarize(Total_Num = sum(Count)) |> 
  pivot_wider(names_from = Name,
              values_from = Total_Num
              ) |> 
  datatable(options = list(lengthChange = FALSE,
                           paging = FALSE),
            class = "cell-border stripe", 
            colnames = c('State',
                         'Alan Count',
                         'Allan Count',
                         'Allen Count'),
            caption =  "TABLE 5: Number of Male Babies Named Alan, Allan, or Allen in California and Pennsylvania")

states_male_allan
```
